---
title: "Airbnb - Bangkok"
author: "Aung Thura Htoo"
date: "2024-08-13"
output: html_document
---

```{r}
#https://insideairbnb.com/bangkok/
```


**Set the Directory, Loaded the data, and "tidyverse"**

```{r}

setwd("D:/me/R-Language/Practice/Dataset")

options(repos = c(CRAN = "https://cran.rstudio.com/"))
install.packages("tidyverse")
library(tidyverse)

# Load the CSV file into a data frame
data <- read.csv("listings_airbnb_Aug2024.csv")
```

**Check the data and Columns**

```{r}
# View the first few rows of the data
head(data)
str(data)

unique_room_type <- unique(data$room_type)
unique_room_type

```

**Distribution of the Room Type**

```{r}
data %>%
  count(room_type) %>%
  ggplot(aes(x = reorder(room_type, -n), y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black", width = 0.7) +
  geom_text(aes(label = n), vjust = -0.5, color = "black", size = 3.5) +
  labs(title = "Distribution of Room Types", x = "Room Type", y = NULL) +
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5))
  
```

**Hosts with multiple listings**

```{r}

top_hosts <- data %>%
  group_by(host_name, room_type) %>%
  summarize(listings_count = n(), .groups = 'drop') %>%
  pivot_wider(
    names_from = room_type,
    values_from = listings_count,
    values_fill = list(listings_count = 0)  # Fill in 0 for missing values
  ) %>%
  mutate(
    `Listings` = `Entire home/apt` + `Private room` + `Shared room` + `Hotel room`
  ) %>% arrange(desc(Listings))

top_hosts

```

**Availability Distribution for Short-Term vs Long-Term Rentals**

```{r}

short_term <- data %>% filter(minimum_nights <= 7)
long_term <- data %>% filter(minimum_nights > 7)


ggplot() +
  geom_histogram(data = short_term, aes(x = availability_365, fill = 'Short-Term'), bins = 30, alpha = 0.5) +
  geom_histogram(data = long_term, aes(x = availability_365, fill = 'Long-Term'), bins = 30, alpha = 0.5) +
  labs(title = "Availability Distribution for Short-Term vs Long-Term Rentals",
       x = "Availability (days per year)",
       y = "Count") +
  scale_fill_manual(values = c('Short-Term' = 'blue', 'Long-Term' = 'red')) +
  theme_minimal()

```

**Mean, Median, and Avg_availability of short-term vs long-term rentals**

```{r}
summary_short_term <- short_term %>%
  summarise(average_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE),
            avg_availability = mean(availability_365, na.rm = TRUE))

summary_long_term <- long_term %>%
  summarise(average_price = mean(price, na.rm = TRUE),
            median_price = median(price, na.rm = TRUE),
            avg_availability = mean(availability_365, na.rm = TRUE))

summary_short_term
summary_long_term

```

**Clean NA and infinite numbers**

```{r}
sum(!is.finite(data$price))
sum(is.na(data$price))

data_clean <- data %>%
  filter(is.finite(price) & !is.na(price))

str(data_clean)
```

**Boxplot of prices by room type**

```{r}
# Boxplot of prices by room type
data_clean %>% ggplot(aes(x = room_type, y = price)) +
  geom_boxplot(fill = "lightgreen", color = "green") +
  labs(title = "Price by Room Type", x = "Room Type", y = "Price")

```

**Boxplot of prices by room type without outliers**

```{r}
# Boxplot of prices by room type with y-axis limits
data_clean %>% ggplot(aes(x = room_type, y = price)) +
  geom_boxplot(fill = "lightgreen", color = "green") +
  labs(title = "Price by Room Type", x = "Room Type", y = "Price") +
  coord_cartesian(ylim = c(0, 6000))

```

------------------------------------------------------------------------

**Scatter plot of price vs. number of reviews**

```{r}
# Scatter plot of price vs. number of reviews
data_clean %>%
  ggplot(aes(x = number_of_reviews, y = price)) +
  geom_point() +
  labs(title = "Price vs. Number of Reviews", x = "Number of Reviews", y = "Price")+ 
  coord_cartesian(ylim = c(0, 10000))

# Compute correlation
cor(data_clean$price, data_clean$number_of_reviews, use = "complete.obs")

```

**Number of Listings by top 15 Neighborhood**

```{r}
# Count of listings by neighborhood and select top 15
neighborhood_counts <- data_clean %>%
  group_by(neighbourhood) %>%
  summarise(count = n()) %>%
  slice_max(order_by = count, n = 15)
neighborhood_counts

# Bar plot of listing counts by neighborhood, arranged in descending order
neighborhood_counts %>% ggplot(aes(x = reorder(neighbourhood, -count), y = count)) +
  geom_bar(stat = "identity", fill = "lightcoral", color = "darkred") +
  labs(title = "Number of Listings by Neighborhood", x = "Neighborhood", y = "Number of Listings") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

**Top 15 Average Price by Neighborhood**

```{r}
# Average price by neighborhood
neighborhood_avg_price <- data_clean %>%
  group_by(neighbourhood) %>%
  summarise(avg_price = mean(price, na.rm = TRUE))%>%
  slice_max(order_by = avg_price, n = 15)

# Bar plot of average price by neighborhood
neighborhood_avg_price %>% ggplot(aes(x = reorder(neighbourhood, -avg_price), y = avg_price)) +
  geom_bar(stat = "identity", fill = "lightblue", color = "blue") +
  labs(title = "Average Price by Neighborhood", x = "Neighborhood", y = "Average Price") +
  coord_cartesian(ylim = c(0, 10000)) +  # Adjust y-axis as needed
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```
